Reproducibility in plant pathology: where do we stand and a way forward

### 2022-05-01 analysis/paper/paper.Rmd
Revise text about results based on new analysis

Only `r as.character(english(length(which(rrpp$reproducibility_score == 100))))` articles scored '100%' or fully reproducible (Figure \@ref(fig:reproScore)).

*Physiological and Molecular Plant Pathology* was the only journal to show a negative effect on the reproducibility score, the analysis was unable to detect any effect of any other journal titles.

There was no effect of article class or impact factor found.

>>>>

There were `r length(which(rrpp$reproducibility_score == 100))` (`r round(length(which(rrpp$reproducibility_score == 100))/nrow(rrpp), 2) * 100`%) articles that scored 100% or were classed as fully reproducible (Figure \@ref(fig:reproScore)).
`r toTitleCase(as.character(english::english(length(which(rrpp$reproducibility_score == 0)))))` (`r round(length(which(rrpp$reproducibility_score == 0))/nrow(rrpp), 2) * 100`%) of articles were scored at 0% out of a possible 100% for reproducibility (Figure \@ref(fig:reproScore)).
The mean value was `r round(mean(rrpp$reproducibility_score), 1)`% and the median value was `r round(median(rrpp$reproducibility_score), 1)`%.

The analysis was unable to detect any effect of journal titles on reproducibility scores.

There was no effect of journal title, article class or impact factor found.
